Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-21 paper.qmd
Added future work for the discussion

In conclusion, while our method effectively captures and represents high-dimensional data structures, further enhancements could involve introducing approaches to diagnose the fitted model. These improvements would help in creating a more accurate representation of the data when \gD{} layout is inadequate.

>>>>

There are many avenues for future work. First, the development of
evaluation metrics is important for NLDR. We introduced a qualitative approach. But having a quantitative measure also will be useful for various application domains. Second, one could use our approach to create an approach for tuning (hyper-)parameters.  Another direction for future work is to introduce approaches to diagnose the fitted model. Finally, one can think of designing a new NLDR method by following the binning in high-dimensions.

<!-- In conclusion, while our method effectively captures and represents high-dimensional data structures, further enhancements could involve introducing approaches to diagnose the fitted model. These improvements would help in creating a more accurate representation of the data when \gD{} layout is inadequate. -->
